Mendelian randomization for causal inference in Genome-wide association studies

### 2022-02-01 mr-review-outline.Rmd
minor text changes

Estimation and testing for unknown parameters proceeds in one of several methods.

@@

@@

Recognizing that many

@@

@@

>>>>

Estimation and testing for unknown parameters proceeds in one of several approaches.

@@

Sensitivity analysis is recommended and widely used in MR studies because of the inability to verify the three MR assumptions.

@@

Recognizing that many genetic markers collectively may affect a trait, investigators 
adapted single-instrument MR methods to accommodate multiple genetic markers.

@@

Linkage disequilibrium, which refers to genotype correlations for genetic markers 
that are near each other, manifests as horizontal pleiotropy in MR studies.

@@

## MR with summary statistics (Morrison et al.)
